EinsteinPy: Python for General Relativity\footnote{Released on January, 8th, 2018}

### 2019-07-10 paper.tex
contributors added

The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with varieties of gravitational physics problems. The most important and central quantity in all of the general relativity is the metric tensor which defines the background geometry of spacetime on which all the dynamics happen. EinsteinPy provides class metric

>>>>

The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with varieties of gravitational physics problems. The most important and central quantity in all of the general relativity is the metric tensor $g_{\mu\nu}$ which defines the background geometry of spacetime on which all the dynamics happen. Informally the problem that packages of numerical relativity tend to solve is that we have a system (or matter field) defined by energy-momentum tensor $T_{\mu\nu}$ and we want to solve for the $g_{\mu\nu}$ such that it satifies the following Einstein's field equation
\[
R_{\mu\nu} - \frac{1}{2}Rg_{\mu\nu} + \Lambda g_{\mu\nu} = \frac{8\pi G}{c^4}T_{\mu\nu}
\]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar $\Lambda$ is cosmological constant. All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation is terms involving $g_{\mu\nu}$ and on the right hand side is the matter field terms which only characterize the distribution of matter because of which the spacetime geometry is curved.\\
EinsteinPy provides a core module: metric which has core data types of various metric tensors some which includes Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are exact solution of field equation for very specific matter distributions). The immediate functionalities which comes along with this module is solution of geodesic equations. The module has coupled integration with coordinates module which deals with different coordinate systems transformations\footnote{more on this in the 'coordinates' section}. Another core data types is in the plotting module which handles all the plotting, rendering, animation and simulation related methods and provides a user friendly interfacing of plots. One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremly important in the formalism of general relativity and many begineers find it  
